Optimal strategies in mental rotation tasks

### 2013-05-13 man/final-project.tex
Caption for simple models figure

\begin{figure}[t]
  \centering
  \begin{subfigure}[b]{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../figures/li_regression.pdf}
    \caption{Na\"ive model}
    \label{fig:li}
  \end{subfigure}
  \begin{subfigure}[b]{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../figures/vm_regression.pdf}
    \caption{Parametric model}
    \label{fig:vm}
  \end{subfigure}
  \caption{\TODO{}}
\end{figure}

>>>>

\begin{figure}[t]
  \centering
  \begin{subfigure}[b]{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../figures/li_regression.pdf}
    \caption{Na\"ive model}
    \label{fig:li}
  \end{subfigure}
  \begin{subfigure}[b]{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../figures/vm_regression.pdf}
    \caption{Parametric model}
    \label{fig:vm}
  \end{subfigure}
  \caption{\textbf{Simple methods of estimating $S$.} In both cases,
    hill-climbing search is used until a maxima is found (in this
    case, at approximately $\frac{\pi}{6}$). The sampled points
    $\mathbf{R}$ (red circles) are then used to estimate $S$ (black
    lines are the true $S$, red lines are the estimate). \textbf{(a)}
    Linear interpolation. The overall estimate of $Z$ here will be too
    low, but certain angles will have a disproportionate contribution
    (e.g., between $\frac{\pi}{4}$ and $\frac{3\pi}{4}$. \textbf{(b)}
    Best fit of scaled Von Mises PDF parameters. As in (a), $Z$ will
    be underestimated. However, the fit around the maximum near
    $\frac{\pi}{6}$ is much more accurate.}
  \label{fig:simple-models}
\end{figure}
